Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-09-23 paper/paper.Rmd
revised custom_cv section

Support for user-defined partitioning strategies is built into \pkg{mlr3} directly.
In this so-called "Custom CV", users are able to supply an external factor vector with the same length as number of observations.
This partitioning concept should not be mistaken with "group-level resampling" (section \@ref(sec:group-level)), which conducts additional combination of data splits and performs CV at the block level.
Each level of the factor vector will result in one partition.
Alternatively to supplying an external factor vector, the name of a feature (type `character`) present within the task can be supplied via argument `col`.

The following example was taken from `sperrorest::partition_factor()` because the resulting partitions separate nicely from each other in a visual way.

>>>>

Support for user-defined partitioning strategies is built into \pkg{mlr3} directly.
In this so-called "Custom CV", users supply a factor variable, each level of which defines a partition.
<!-- AB: I think we can omit this sentence, otherwise we would have to repeat it for the other LOBO methods as well. Here we're in the leave-ONE-something-out section. -->
<!--
This partitioning concept should not be mistaken with "group-level resampling" (section \@ref(sec:group-level)), which conducts additional combination of data splits and performs CV at the block level.
-->
The factor variable can either be specified through a factor vector of the same length as number of observations, or by passing the name of a feature of type `character` within the task (argument `col`).
The following simple example from `sperrorest::partition_factor()` creates altitudinal zones that define the spatial partitions.
